>

### 2020-09-24 manuscript/manuscript.Rmd
Clean up model estimates, with cemeteries eliminated
This closes #10

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
```{r slx-sdem, results = "asis"}
slx_coefs <- lapply(slx_vs_sdem, function(x) tidy(x, conf.int = TRUE))
slx_stats <- lapply(slx_vs_sdem, glance)
tab <- right_join(slx_coefs$SLX, slx_coefs$SDEM, by = "term") %>%
  transmute(term, estimate.x, conf.low.x, conf.high.x, space = " ",
                  estimate.y, conf.low.y, conf.high.y) %>%
  mutate(term = unlist(cm))

xtab <- xtable(tab, digits = 4)
print(xtab, include.rownames = FALSE, include.colnames = F,
      sanitize.text.function = identity, floating = F, only.contents = T, hline.after = NULL)
```
\midrule
Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
\bottomrule
\end{tabular}
\end{table*}

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
coefficients for three models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels} of the Supplementary Material. Each of the three
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized directionality. That is, residents living in tracts 
with increased utility-based accessibility to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the 2
estimated utility-based coefficients, moving from the least-accessible tract
($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .15` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .01` and `r 6 * .3` percentage points.

The 10-minute walk buffer is considerably less useful at isolating the effects
of park "access" on physical activity rates. As so few tracts are located
outside of the buffer, the standard error of the estimated effect is large and implies
an effect on activity rates anywhere from a loss of `r 6 * .18` percentage points
to a gain of `r 6 * 1.35`.

>>>>

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
```{r slx-sdem, results = "asis"}
class(slx_vs_sdem$SLX) <- "lm"
slx_coefs <- lapply(slx_vs_sdem, function(x) tidy(x, conf.int = TRUE))
slx_stats <- lapply(slx_vs_sdem, glance)
tab <- right_join(slx_coefs$SLX, slx_coefs$SDEM, by = "term") %>%
  transmute(term, estimate.x, conf.low.x, conf.high.x, space = " ",
                  estimate.y, conf.low.y, conf.high.y) %>%
  mutate(term = unlist(cm))

xtab <- xtable(tab, digits = 4)
print(xtab, include.rownames = FALSE, include.colnames = F,
      sanitize.text.function = identity, floating = F, only.contents = T, hline.after = NULL)
```
\midrule
Log Likelihood & \multicolumn{3}{c}{$`r logLik(slx_vs_sdem$SLX)`$} & & \multicolumn{3}{c}{$`r logLik(slx_vs_sdem$SDEM)`$}\\
Num.Obs.       & \multicolumn{3}{c}{$`r nobs(slx_vs_sdem$SLX)`$}   & & \multicolumn{3}{c}{$`r nrow(slx_vs_sdem$SDEM$X)`$}\\
\bottomrule
\end{tabular}
\end{table*}

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
coefficients for two models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels} of the Supplementary Material. Each of the two
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized direction That is, residents living in tracts 
with increased utility-based accessibility to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the two
estimated utility-based coefficients, moving from the least-accessible tract
($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .22` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.

In contrast, 10-minute walk buffer is considerably less useful at isolating the effects
of park "access" on physical activity rates. As so few tracts are located
outside of the buffer, the standard error of the estimated effect is large and implies
an effect on activity rates anywhere from a loss of `r .18` percentage points
to a gain of `r 1.35`.
